Temperature Effects on Surface Sulfur Dioxide

### 2011-08-24 Background.tex
Working out edits. Added all figure captions.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/double-cycle-type2-small.png}
		\caption{}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/double-cycle-type2-small.png}
		\caption{During the course of MD, the covalent and intermolecular bonds between a \suldiox~and the hydrating waters may form into a ring, resulting in a cyclic hydrate structure. Depicted here is one example of such a cyclic structure, formed by the covalent SO and OH bonds of the two molecule types, and the intermolecular hydrogen bonds, and S-O$_{H_2O}$ interactions. The atoms involved are the S (yellow), O (red), and H (white).}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

### 2011-08-24 Coordination-Results.tex
Working out edits. Added all figure captions.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-transitions.png}
		\caption{}
		\label{fig:coordination-transitions}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-lifespans.png}
		\caption{}
		\label{fig:coordination-lifespans}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-transitions.png}
		\caption{The bonding coordinations of \suldiox~on a water surface rapidly change as bonds break and form throughout the MD trajectories. Depicted here is a graph of the bonding coordinations, shown as colored nodes of varying size. Larger and more darkly colored coordination nodes are those more often encountered during MD (see Figure \ref{fig:bonding-coordinations}). The directed edges between the nodes represent the number of times the coordination transition occured. Thicker lines correspond to a greater number of transitions between coordinations. The number of time a given transition occured is labeled to the right of the corresponding line.}
		\label{fig:coordination-transitions}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-lifespans.png}
		\caption{Given that certain bonding coordinations of the surface \suldiox~are more often encountered than others (see Figure \ref{fig:bonding-coordinations}), the plot here shows the time spent in each bonding coordination. Each point in the plot represents a single span of simulation time that the \suldiox~had the given coordination. The amount of time spent corresponds to the vertical position along the lifespan axis, in ps.}
		\label{fig:coordination-lifespans}
	\end{center}
\end{figure}

### 2011-08-24 Cycle-Results.tex
Working out edits. Added all figure captions.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}
The plot in Figure \ref{fig:cycle-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. The plot is based on two criteria for determining if a cyclic structure has formed. (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on order of discovery. The \suldiox~will be inevitably involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as the most affect the \suldiox~bonding and hydrating behaviors.

It is remarkable that the difference of the time spent in a cyclic structure between the two temperatures is 15\% (42\% cold, 57\%hot). The hot \suldiox~spends well over half of the simulated time bound as one of the hydrate cycles, and the cold \suldiox~spends just under half of the time as such. Thus, in addition to having found the most likely bonding coordination during the simulated life of \suldiox, we have also found that the hydrates of the \suldiox~form a cyclic structure for much of the time it is bound to the water surface.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/cycle-debouncing-small.png}
		\caption{}
		\label{fig:debouncing}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/cyclic-lifespans-inset-small.png}
		\caption{}
		\label{fig:cycle-lifespans}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{Cyclic hydrate structures form throughout the MD simulations involving the \suldiox~and one or more water molecules. Shown here are the different cycles by number of water (up to 4), and their occurence rate as a percentage of the total simulation time. The far right part of the plot shows the contributions of the two types of triple-water cycles (see Figure \ref{fig:type-3-varieties}). The cycles had to meet the ``minimally-SO'' bonding criteria (at least one bond to the sulfur and one oxygen bond on the \suldiox) to be used in the analysis.}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}

The plot in Figure \ref{fig:cyclic-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. The plot is based on two criteria for determining if a cyclic structure has formed. (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on order of discovery. The \suldiox~will be inevitably involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as the most affect the \suldiox~bonding and hydrating behaviors.

It is remarkable that the difference of the time spent in a cyclic structure between the two temperatures is 15\% (42\% cold, 57\% hot). The hot \suldiox~spends well over half of the simulated time bound as one of the hydrate cycles, and the cold \suldiox~spends just under half of the time as such. Thus, in addition to having found the most likely bonding coordination during the simulated life of \suldiox, we have also found that the hydrates of the \suldiox~form a cyclic structure for much of the time it is bound to the water surface.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/cycle-debouncing-small.png}
		\caption{The dynamic environment of the water surface causes rapid breaking and formation of bonds to the \suldiox, and to waters involved in the cyclic hydrating structures. A ``debouncing'' procedure was developed (described above in the text) to account for the very brief ($<$ 20 fs) breaks to the cyclic structure. A time function, $C(t)$ (dashed black), shows if the bonding distance criteria are met for all members of the cyclic hydrate structure. A gaussian smoothing window was then used to produce $C_s(t)$ (red), which was then used with a cutoff criteria to give the ``debounced'' cycle formation time function, $f(t)$ (green).}
		\label{fig:debouncing}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/cyclic-lifespans-inset-small.png}
		\caption{The lifetime of a cyclic hydrate structure after it forms, and before it distorts in shape due to the movement of the liquid surface molecules, is most often short ($<$ 1 ps). Shown here is a plot of cycle hydrate structure lifetimes after having applied the ``debouncing'' procedure (described in the text). Both cold (blue) and hot (red) simulations are graphed. The inset expands the view of the region above 1 ps.}
		\label{fig:cycle-lifespans}
	\end{center}
\end{figure}
